A Bayesian search to find \\high-mass black holes in LIGO data

### 2020-08-20 main.tex
Fix compilation errors

\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{hyperref}% add hypertext capabilities
\usepackage{graphicx} % Include figure files
\graphicspath{{Figures/}} %Setting the graphicspath

@@

% PyCBC asks for the 5 citations:
% http://pycbc.org/pycbc/latest/html/credit.html#searches-for-compact-binary-coalescence
Following \citet{bcr_paper}, the \bcr is an odds ratio of the coherent signal hypotheses $mathcal{H_S}$ and the incoherent instrumental feature hypothesis $mathcal{H_I}$. It is given by
\begin{equation}
BCR = \frac{\alpha Z^S}{\Pi^D_{i=1}[\beta Z^G_i + (1-\beta)Z^N_i]}\ .
\end{equation}
The numerator is the probability of obtaining a coherent signal, where $Z^S$ is the evidence for $\mathcal{H_S}$ and $\alpha$ is the prior odds for obtaining a signal $\alpha=P(\mathcal{H_S})/P(\mathcal{H_I})$. The denominator is the probability of obtaining an incoherent glitch or noise amongst the network of $D$ detectors, where $Z_G_i$ and $Z_N_i$ are the evidence for obtaining a glitch in detector $i$ and the evidence for obtaining just noise in detector $i$.

>>>>

\usepackage{aas_macros}

\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{booktabs}
\usepackage{xspace} 
\usepackage{bm}% bold math
\usepackage{hyperref}% add hypertext capabilities
\usepackage{graphicx} % Include figure files
\graphicspath{{Figures/}} %Setting the graphicspath

@@

% PyCBC asks for the 5 citations:
% http://pycbc.org/pycbc/latest/html/credit.html#searches-for-compact-binary-coalescence
Following \citet{bcr_paper}, the \bcr is an odds ratio of the coherent signal hypotheses $\mathcal{H_S}$ and the incoherent instrumental feature hypothesis $\mathcal{H_I}$. It is given by
\begin{equation}
BCR = \frac{\alpha Z^S}{\Pi^D_{i=1}[\beta Z^G_i + (1-\beta)Z^N_i]}\ .
\end{equation}
The numerator is the probability of obtaining a coherent signal, where $Z^S$ is the evidence for $\mathcal{H_S}$ and $\alpha$ is the prior odds for obtaining a signal $\alpha=P(\mathcal{H_S})/P(\mathcal{H_I})$. The denominator is the probability of obtaining an incoherent glitch or noise amongst the network of $D$ detectors, where $Z_{Gi}$ and $Z_{Ni}$ are the evidence for obtaining a glitch in detector $i$ and the evidence for obtaining just noise in detector $i$.
